# Management 

## Reference Points

```{r, echo=FALSE, results='asis'}
filein = file.path(getwd(), "shared_text",'reference_points.Rmd')
read_child(filein)
```

## Unresolved Problems and Major Uncertainties

```{r, echo=FALSE, results='asis'}
filein = file.path(getwd(), "shared_text",'unresolved_problems_uncertainties.Rmd')
read_child(filein)
```

## Harvest Projections and Decision Tables

The forecast of stock abundance and yield was developed using the base model. The total catches in 2021 and 2022 were set at 10,000 mt, well below the adopted 50,000 mt ACL for those year, based on recommendations from the Groundfish Management Team (GMT). These assumed removals are likely higher than what the true removals may be in 2021 and 2022 but have limited impact in the stock status and future removals during the projected periord in the base model. The exploitation rate for 2023 and beyond is based upon an SPR of 30 percent and the 25:5 harvest control rule. The average exploitation rates, across recent years, by fleet were used to distribute catches during the forecast period. The ABC values were estimated using a category 1 time-varying $\sigma_y$ starting at 0.50 combined with a P* value of 0.45. The catches during the projection period, 2023 - 2032 were set equal to the year-specific ABC using the current flatfish harvest control rule, 25:5 (Table \ref{tab:es-project}). 

The axes of uncertainty  in the decision table is based on the uncertainty around female natural mortality. Uncertainty in the forecasts is based upon the category 1 default uncertainty of $\sigma$ = 0.50. The default $\sigma$ value was used to identify the 12.5 and 87.5 percentiles of the asymptotic standard deviation for the current year, `r endyr+1`, spawning biomass from the base model to identify the low and high states of nature (i.e., 1.15 standard deviations corresponding to the 12.5 and 87.5 percentiles). Once the `r endyr + 1` spawning biomass for the low and high states of nature were identified a search across female natural mortality values were done to attain the current year spawning biomass values. The female natural mortality values that corresponded with the lower and upper percentiles were 0.084 yr^-1^ and 0.126 yr^-1^. 

Initial explorations were conducted using the model estimated uncertainty around `r endyr + 1` spawning biomass of $\sigma$ = `r round(model$Pstar_sigma,2)` rather than the higher default $\sigma$ value.  However, the range of the low and high states of nature relative to the base model were determined to not adequately capture uncertainty based on feedback received during the STAR panel review. The model estimated $\sigma$ around the `r endyr +1` spawning biomass only captures model uncertainty which is an underestimate of the true uncertainty around the stock size. Applying a higher $\sigma$ value allowed the low and high states of nature to capture a larger uncertainty which may be more in line with the cumalative model and structural uncertainty. It was noted that the low and high states of nature results in catchability values (low state of nature catchability = 2.0 and high state of nature catchability = 0.56) for the \gls{s-wcgbt} that were factors higher or lower than the base model catchability (`r round(exp(model$parameters[model$parameters$Label == "LnQ_base_NWFSC_WCGBT(6)", 3]), 3)`). Interpreting values of catchability comes with inherent challenges due to changes in other key model parameters (e.g., selectivity). 

Three alternative catch streams were created for the decision table. The first option uses ABC values based on a category 1 $\sigma_y$ starting at 0.50 and increasing annually combined with a P$^*$ value of 0.45. The two alternative catch streams assume fixed catch of either 7,000 or 20,000 mt for the 10 year projection period. All of these options assume full attainment of the catch values.  

Across the low and high states of nature and across alternative future harvest scenarios the fraction of unfished ranges between 0.023 - 0.895 by the end of the 10 year projection period (Table \ref{tab:dec-tab}). The low state of nature assuming full ABC removals results in a nearly depleted stock at the end of the time series.  This is due to the assumption or removing the full ABC derived from the base model to the low state of nature which had an overall lower unfished spawning biomass associated with a low natural mortality value which results in a more depleted stock in `r endyr+1` relative to the base model. 


## Evaluation of Scientific Uncertainty

```{r, echo=FALSE, results='asis'}
filein = file.path(getwd(), "shared_text",'scientific_uncertainty.Rmd')
read_child(filein)
```

## Regional Management Considerations

Currently `r spp` are managed using coastwide harvest specifications; therefore, this assessment does not provide a recommended method for allocating harvests regionally. There is currently no genetic evidence that there are distinct biological stocks of `r spp` off the U.S. west coast. The limited historical tagging data available describing adult movement suggests that there may be significant movement across depth but limited movement across latitude.

## Research and Data Needs

```{r, echo=FALSE, results='asis'}
filein = file.path(getwd(), "shared_text",'research_and_data_needs.Rmd')
read_child(filein)
```